Figures

### 2025-08-07 docs/code/08_figures-tables.Rmd
First mansucript draft

lnRR_design_plot <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
 scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "lnRR")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0),
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  ) + scale_x_discrete(labels = c("Non-aromatic Vs. Aromatic","No material Vs. Aromatic", "No material Vs. Non-Aromatic"))

SMDH_design_plot <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
    trunk.size = 0.25,
    branch.size = 1,
    twig.size = 0.5,
    alpha = 0.2,
    xlab ="") +
 scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  labs(x = "",
       y = "SMD(H)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position = "none",
    # legend.position.inside = c(0.98, 0.05),
    # legend.justification = c(1, 0),
    # legend.direction = "horizontal",
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1)
  )

@@

# Combine using patchwork
Figure_design_time_gnm_addition <- ((lnRR_design_plot + SMDH_design_plot) /
                               (lnRR_time_gnm_addition_plot + SMDH_time_gnm_addition_plot)) +
  plot_annotation(tag_levels = "A")

@@

@@

lnRR_small_study_bubble<-orchaRd::bubble_plot(mod_results(lnRR_small_study,
                     mod="sqrt_effective_n_inv",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID") +
  scale_colour_manual(values ="mediumpurple4") +
  scale_fill_manual(values = "mediumpurple4") +
  labs(y = "Effect size (lnRR)",
       x = expression(sqrt(1 / N[effective])))+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

SMDH_small_study_bubble<-orchaRd::bubble_plot(mod_results(SMDH_small_study,
                     mod="sqrt_effective_n_inv",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID") +
  scale_colour_manual(values ="mediumpurple4") +
  scale_fill_manual(values = "mediumpurple4") +
  labs(y = "Effect size (SMDH)",
       x = expression(sqrt(1 / N[effective])))+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

@@

lnRR_decline_eff_bubble<-orchaRd::bubble_plot(mod_results(lnRR_decline_eff,
                     mod="year_MeanCenter",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID")+
  scale_colour_manual(values ="#218833") +
  scale_fill_manual(values = "#218833") +
  labs(y = "Effect size (lnRR)",
       x = "Publication Year (Mean Cenetered)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

SMDH_decline_effect_bubble<-orchaRd::bubble_plot(mod_results(SMDH_decline_eff,
                     mod="year_MeanCenter",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID")+
  scale_colour_manual(values ="#218833") +
  scale_fill_manual(values = "#218833") +
  labs(y = "Effect size (SMDH)",
       x = "Publication Year (Mean Cenetered)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

@@

# -------- TABLES ———-

@@

pacman::p_load(gt,dplyr,metafor)

@@

@@

SA_intercept_only <- tibble::tibble(
  effect_size = c("lnRR","lnRR","lnRR","SMDH","SMDH","SMDH","SMDH"),
  data_used = c("Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Without the cases where SMDH was calculated from inferential statistics"),

  Estimate = c(SA_lnRR_flagged$b[1],
               SA_lnRR_no_missingES$b[1],
               SA_lnRR_flagged_no_missingES$b[1],
               SA_SMDH_flagged$b[1],
               SA_SMDH_no_missingES$b[1],
               SA_SMDH_flagged_no_missingES$b[1],
               SA_SMDH_no_inferential$b[1]),

  CI_Lower = c(SA_lnRR_flagged$ci.lb,
               SA_lnRR_no_missingES$ci.lb,
               SA_lnRR_flagged_no_missingES$ci.lb,
               SA_SMDH_flagged$ci.lb,
               SA_SMDH_no_missingES$ci.lb,
               SA_SMDH_flagged_no_missingES$ci.lb,
               SA_SMDH_no_inferential$ci.lb),

  CI_Upper = c(SA_lnRR_flagged$ci.ub,
               SA_lnRR_no_missingES$ci.ub,
               SA_lnRR_flagged_no_missingES$ci.ub,
               SA_SMDH_flagged$ci.ub,
               SA_SMDH_no_missingES$ci.ub,
               SA_SMDH_flagged_no_missingES$ci.ub,
               SA_SMDH_no_inferential$ci.ub),

  PI_Lower = c(predict(SA_lnRR_flagged)$pi.lb,
               predict(SA_lnRR_no_missingES)$pi.lb,
               predict(SA_lnRR_flagged_no_missingES)$pi.lb,
               predict(SA_SMDH_flagged)$pi.lb,
               predict(SA_SMDH_no_missingES)$pi.lb,
               predict(SA_SMDH_flagged_no_missingES)$pi.lb,
               predict(SA_SMDH_no_inferential)$pi.lb),

  PI_Upper = c(predict(SA_lnRR_flagged)$pi.ub,
               predict(SA_lnRR_no_missingES)$pi.ub,
               predict(SA_lnRR_flagged_no_missingES)$pi.ub,
               predict(SA_SMDH_flagged)$pi.ub,
               predict(SA_SMDH_no_missingES)$pi.ub,
               predict(SA_SMDH_flagged_no_missingES)$pi.ub,
               predict(SA_SMDH_no_inferential)$pi.ub),

  P_value = c(SA_lnRR_flagged$pval,
              SA_lnRR_no_missingES$pval,
              SA_lnRR_flagged_no_missingES$pval,
              SA_SMDH_flagged$pval,
              SA_SMDH_no_missingES$pval,
              SA_SMDH_flagged_no_missingES$pval,
              SA_SMDH_no_inferential$pval),

  Q_value = c(SA_lnRR_flagged$QE,
              SA_lnRR_no_missingES$QE,
              SA_lnRR_flagged_no_missingES$QE,
              SA_SMDH_flagged$QE,
              SA_SMDH_no_missingES$QE,
              SA_SMDH_flagged_no_missingES$QE,
              SA_SMDH_no_inferential$QE),

  k_effect_sizes = c(SA_lnRR_flagged$k,
        SA_lnRR_no_missingES$k,
        SA_lnRR_flagged_no_missingES$k,
        SA_SMDH_flagged$k,
        SA_SMDH_no_missingES$k,
        SA_SMDH_flagged_no_missingES$k,
        SA_SMDH_no_inferential$k),

  n_studies = c(length(SA_lnRR_flagged$s.levels.f[[1]]),
                      length(SA_lnRR_no_missingES$s.levels.f[[1]]),
                      length(SA_lnRR_flagged_no_missingES$s.levels.f[[1]]),
                      length(SA_SMDH_flagged$s.levels.f[[1]]),
                      length(SA_SMDH_no_missingES$s.levels.f[[1]]),
                      length(SA_SMDH_flagged_no_missingES$s.levels.f[[1]]),
                      length(SA_SMDH_no_inferential$s.levels.f[[1]])
))

# Combine CI and PI into a single column each for compactness
SA_intercept_only <- SA_intercept_only %>%
  mutate(
    CI = paste0("[", sprintf("%.3f", CI_Lower), ", ", sprintf("%.3f", CI_Upper), "]"),
    PI = paste0("[", sprintf("%.3f", PI_Lower), ", ", sprintf("%.3f", PI_Upper), "]"),
    P_value = scales::pvalue(P_value),
    Q_value = sprintf("%.2f", Q_value)
  ) %>%
  select(
    effect_size,
    data_used,
    Estimate,
    CI,
    PI,
    P_value,
    Q_value,
    k_effect_sizes,
    n_studies
  )

# Let's make this table pretty
SA_intercept_only<-SA_intercept_only%>%
  gt()%>%
  tab_options(
    table.font.size = px(12),
    table.border.top.color = "black",
    table.border.bottom.color = "black",
    heading.title.font.size = px(14),
    heading.subtitle.font.size = px(12),
    column_labels.font.weight = "bold"
  ) %>%
  tab_header(
    title = md("**Summary of Sensitivity Analyses for lnRR and SMDH Intercept-only models**")
  ) %>%
  cols_label(
    effect_size = "Effect Size",
    data_used = "Data used in model",
    Estimate = "Estimate",
    CI = "95% CI",
    PI = "95% PI",
    P_value = "P-value",
    Q_value = "Q value",
    k_effect_sizes = "k (No. of Effect Sizes)",
    n_studies = "n (No. of Studies)"
  ) %>%
  fmt_number(
    columns = c(Estimate),
    decimals = 3
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  tab_options(
    table.font.size = "small",
    heading.title.font.size = 14,
    table.border.top.width = px(2),
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold"
  ) %>%
  opt_table_outline()

#saving as a docx file
gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.docx"))
gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.html"))
```

>>>>

lnRR_design_plot <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(1,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
labs(x = "",
     y = "Effect Size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. non-Aromatic"))

SMDH_design_plot <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(1.5,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794"))+
labs(x = "",
     y = "Effect Size (SMDH)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. Non-aromatic"))

##-----------------------------------------------------------------------------

# Now the cropped figures for the main manuscript

##-----------------------------------------------------------------------------

lnRR_design_plot_cropped <-
  orchard_plot(mod_results(
      lnRR_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
  trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
  k.pos = c(0.4,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-0.6, 0.6)) +
labs(x = "",
     y = "Effect Size (lnRR)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. Non-aromatic"))

SMDH_design_plot_cropped <-
  orchard_plot(mod_results(
      SMDH_design,
      mod = "comparision_type",
      group = "paper_ID"
    ),
   trunk.size = 0.5,
  branch.size = 1.3,
  twig.size = 0.5,
  alpha = 0.4,
  fill = T,
    k.pos = c(1.9,0.6,0.6),
  xlab ="") +
  scale_colour_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_fill_manual(values = c("#FF8CAE", "#003A7D", "#7E4794")) +
  scale_y_continuous(limits = c(-2.3, 2.3)) +
labs(x = "",
     y = "Effect Size (SMDH)")+
  theme(panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.position.inside = c(0.99, 0.01),
    legend.justification = c(1, 0), 
    legend.direction = "horizontal",
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.title = element_text(size = 6),
    legend.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))+ 
  scale_x_discrete(labels = c("Non-aromatic\nVs. aromatic","No material\nVs. aromatic", "No material\nVs. non-Aromatic"))

@@

# Combine using patchwork
Figure_design_time_gnm_addition<- ((lnRR_design_plot + SMDH_design_plot) /
                               (lnRR_time_gnm_addition_plot + SMDH_time_gnm_addition_plot)) +
  plot_annotation(tag_levels = "A")

@@

##-----------------------------------------------------------------------------

# Now the cropped figures for the main manuscript

##-----------------------------------------------------------------------------

## I am going to remove the y ticks from the SMDH plots to make it smaller..
SMDH_design_plot_cropped <- SMDH_design_plot_cropped +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

SMDH_time_gnm_addition_plot_cropped <- SMDH_time_gnm_addition_plot_cropped +
  theme(axis.text.y  = element_blank(),
        axis.title.y = element_blank(),
        axis.ticks.y = element_blank())

# Combine using patchwork
Figure_design_time_gnm_addition_cropped <- ((lnRR_design_plot_cropped + SMDH_design_plot_cropped) /
                               (lnRR_time_gnm_addition_plot_cropped + SMDH_time_gnm_addition_plot_cropped)) +
  plot_annotation(tag_levels = "A")

ggsave(here::here("figures/Figure_design_time_gnm_addition_cropped.png"), plot = Figure_design_time_gnm_addition_cropped, height = 240, width = 250, units = "mm", dpi = 600)

@@

lnRR_small_study_bubble<-orchaRd::bubble_plot(mod_results(lnRR_small_study,
                     mod="sqrt_effective_n_inv",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID") +
  scale_colour_manual(values ="mediumpurple4") +
  scale_fill_manual(values = "mediumpurple4") +
  coord_cartesian(ylim = c(-2.5, 2.5)) +
  labs(y = "Effect size (lnRR)",
       x = expression(sqrt(1 / N[effective])))+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

SMDH_small_study_bubble<-orchaRd::bubble_plot(mod_results(SMDH_small_study,
                     mod="sqrt_effective_n_inv",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID") +
  scale_colour_manual(values ="mediumpurple4") +
  scale_fill_manual(values = "mediumpurple4") +
  coord_cartesian(ylim = c(-10, 7)) +
  labs(y = "Effect size (SMDH)",
       x = expression(sqrt(1 / N[effective])))+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

@@

lnRR_decline_eff_bubble<-orchaRd::bubble_plot(mod_results(lnRR_decline_eff,
                     mod="year_MeanCenter",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID")+
  scale_colour_manual(values ="#218833") +
  scale_fill_manual(values = "#218833") +
  coord_cartesian(ylim = c(-2.5, 2.5)) +
  labs(y = "Effect size (lnRR)",
       x = "Publication Year (Mean Centered)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

SMDH_decline_effect_bubble<-orchaRd::bubble_plot(mod_results(SMDH_decline_eff,
                     mod="year_MeanCenter",
                     group="paper_ID",
                     weights="prop"),
                     group="paper_ID")+
  scale_colour_manual(values ="#218833") +
  scale_fill_manual(values = "#218833") +
  coord_cartesian(ylim = c(-10, 7)) +
  labs(y = "Effect size (SMDH)",
       x = "Publication Year (Mean Centered)")+
    theme(
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 0.8),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title = element_text(size = 14),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(angle = 0, vjust = 0.5, hjust = 1))

@@

# ----- Supplementary Material Table -------

# Loading packages

pacman::p_load(gt,dplyr,metafor)
```

```{r}
#| label: excluded_proxy_table

merged_data_extraction <- read_csv(here::here("data/03_data_cleaning/merged_data_extraction.csv"), show_col_types = F)

dataset_analysis <- read_csv(here::here("data/04_data_analysis/dataset_analysis.csv"), show_col_types = F)

excluded_proxies<- merged_data_extraction %>%
  filter(fulltext_screening == "included") %>%
  filter(proxy_decision== "exclude")%>%
  select(paper_ID, fitness_proxy, proxy_comment) %>%
  distinct() %>%
  group_by(paper_ID) %>%
  summarise(
    `Number of proxies` = n(),
    `Excluded Proxies` = paste(fitness_proxy, collapse = ", "),
    `Reason for Exclusion`= paste(proxy_comment,  collapse = "; "),
    .groups = "drop")

SA_only_proxies <- dataset_analysis %>%
  filter(proxy_decision == "sensitivity-analysis")%>%
  select(paper_ID, fitness_proxy, proxy_comment) %>%
  distinct() %>%
  group_by(paper_ID) %>%
  summarise(
    `Number of proxies` = n(),
    `Excluded Proxies` = paste(fitness_proxy, collapse = ", "),
    `Reason for Exclusion`= paste(proxy_comment,  collapse = "; "),
    .groups = "drop")

# Now binding them together
combined_summary <- bind_rows(
  excluded_proxies %>% mutate(Category = "Completely excluded"),
  SA_only_proxies   %>% mutate(Category = "Sensitivity-analysis only")
) %>%
  arrange(Category, paper_ID)

# Group by category
excluded_proxies <-combined_summary %>%
  gt() %>%
  tab_header(
    title = md("**Excluded Fitness Proxies**")
  ) %>%
  # define row-groups
  tab_row_group(
    group    = "Completely excluded",
    rows     = Category == "Completely excluded"
  ) %>%
  tab_row_group(
    group    = "Sensitivity-analysis only",
    rows     = Category == "Sensitivity-analysis only"
  ) %>%
  # hide the helper column
  cols_hide("Category") %>%
  # relabel columns
  cols_label(
         `paper_ID`             = "Paper ID",
         `Number of proxies`    = "Noumber\nof Proxies",
         `Excluded Proxies`     = "Excluded\nProxies",
         `Reason for Exclusion` = "Reason for Exclusion"
  ) %>%
  fmt_markdown(columns = c(`Excluded Proxies`, `Reason for Exclusion`)) %>%
  opt_align_table_header(align = "left") %>%
  cols_align(
    align   = "left",
    columns = everything()
  ) %>%
  tab_options(
    table.width               = pct(90),
    row.striping.background_color = "#F7F7F7"
  )

# gtsave(
#   data = excluded_proxies,
#   filename = here::here("/tables/excluded_proxies_table.pdf"),
#   expand = 10   # adds a little padding around the table
# )
```

@@

# Loading the models including only published data
SA_lnRR_published<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_published.rds"))
SA_SMDH_published<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_published.rds"))

# Loading the models without Comparison Type 3
SA_lnRR_no_comp3<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_no_comp3.rds"))
SA_SMDH_no_comp3<-readRDS(here::here("model/sensitivity_analysis/SA_SMDH_no_comp3.rds"))

@@

# Loading the model for Geary's Test Passed. There is none for SMDH because we do not know the guideline for SMDH and Geary's Test
SA_lnRR_geary_passed<-readRDS(here::here("model/sensitivity_analysis/SA_lnRR_geary_passed.rds"))

@@

SA_intercept_only <- tibble::tibble(
  effect_size = c("lnRR","lnRR","lnRR","lnRR","lnRR","lnRR",
                  "SMD(H)","SMD(H)","SMD(H)","SMD(H)","SMD(H)","SMDH"),
  data_used = c("Including published data only","Excluding Experimental Design Non-Aromatic Vs. No added material","Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Excluding effect sizes where lnRR failed Geary's Test","Including published data only","Excluding Experimental Design Non-Aromatic Vs. No added material", "Including flagged proxies", "Without those cases where author reported no effect of the treatment", "Including flagged proxies and without the cases with no effect of the treatment", "Without the cases where SMDH was calculated from inferential statistics"),

  Estimate = c(SA_lnRR_published$b[1],
               SA_lnRR_no_comp3$b[1],
               SA_lnRR_flagged$b[1],
               SA_lnRR_no_missingES$b[1],
               SA_lnRR_flagged_no_missingES$b[1],
               SA_lnRR_geary_passed$b[1],
               SA_SMDH_published$b[1],
               SA_SMDH_no_comp3$b[1],
               SA_SMDH_flagged$b[1],
               SA_SMDH_no_missingES$b[1],
               SA_SMDH_flagged_no_missingES$b[1],
               SA_SMDH_no_inferential$b[1]),

  CI_Lower = c(SA_lnRR_published$ci.lb,
               SA_lnRR_no_comp3$ci.lb,
               SA_lnRR_flagged$ci.lb,
               SA_lnRR_no_missingES$ci.lb,
               SA_lnRR_flagged_no_missingES$ci.lb,
               SA_lnRR_geary_passed$ci.lb,
               SA_SMDH_published$ci.lb,
               SA_SMDH_no_comp3$ci.lb,
               SA_SMDH_flagged$ci.lb,
               SA_SMDH_no_missingES$ci.lb,
               SA_SMDH_flagged_no_missingES$ci.lb,
               SA_SMDH_no_inferential$ci.lb),

  CI_Upper = c(SA_lnRR_published$ci.ub,
               SA_lnRR_no_comp3$ci.ub,
               SA_lnRR_flagged$ci.ub,
               SA_lnRR_no_missingES$ci.ub,
               SA_lnRR_flagged_no_missingES$ci.ub,
               SA_lnRR_geary_passed$ci.ub,
               SA_SMDH_published$ci.ub,
               SA_SMDH_no_comp3$ci.ub,
               SA_SMDH_flagged$ci.ub,
               SA_SMDH_no_missingES$ci.ub,
               SA_SMDH_flagged_no_missingES$ci.ub,
               SA_SMDH_no_inferential$ci.ub),

  PI_Lower = c(predict(SA_lnRR_published)$pi.lb,
               predict(SA_lnRR_no_comp3)$pi.lb,
               predict(SA_lnRR_flagged)$pi.lb,
               predict(SA_lnRR_no_missingES)$pi.lb,
               predict(SA_lnRR_flagged_no_missingES)$pi.lb,
               predict(SA_lnRR_geary_passed)$pi.lb,
               predict(SA_SMDH_published)$pi.lb,
               predict(SA_SMDH_no_comp3)$pi.lb,
               predict(SA_SMDH_flagged)$pi.lb,
               predict(SA_SMDH_no_missingES)$pi.lb,
               predict(SA_SMDH_flagged_no_missingES)$pi.lb,
               predict(SA_SMDH_no_inferential)$pi.lb),

  PI_Upper = c(predict(SA_lnRR_published)$pi.ub,
               predict(SA_lnRR_no_comp3)$pi.ub,
               predict(SA_lnRR_flagged)$pi.ub,
               predict(SA_lnRR_no_missingES)$pi.ub,
               predict(SA_lnRR_flagged_no_missingES)$pi.ub,
               predict(SA_lnRR_geary_passed)$pi.ub,
               predict(SA_SMDH_published)$pi.ub,
               predict(SA_SMDH_no_comp3)$pi.ub,
               predict(SA_SMDH_flagged)$pi.ub,
               predict(SA_SMDH_no_missingES)$pi.ub,
               predict(SA_SMDH_flagged_no_missingES)$pi.ub,
               predict(SA_SMDH_no_inferential)$pi.ub),

  P_value =  c(SA_lnRR_published$pval,
               SA_lnRR_no_comp3$pval,
               SA_lnRR_flagged$pval,
               SA_lnRR_no_missingES$pval,
               SA_lnRR_flagged_no_missingES$pval,
               SA_lnRR_geary_passed$pval,
               SA_SMDH_published$pval,
               SA_SMDH_no_comp3$pval,
               SA_SMDH_flagged$pval,
               SA_SMDH_no_missingES$pval,
               SA_SMDH_flagged_no_missingES$pval,
               SA_SMDH_no_inferential$pval),

  Q_value = c(SA_lnRR_published$QE,
               SA_lnRR_no_comp3$QE,
               SA_lnRR_flagged$QE,
               SA_lnRR_no_missingES$QE,
               SA_lnRR_flagged_no_missingES$QE,
               SA_lnRR_geary_passed$QE,
               SA_SMDH_published$QE,
               SA_SMDH_no_comp3$QE,
               SA_SMDH_flagged$QE,
               SA_SMDH_no_missingES$QE,
               SA_SMDH_flagged_no_missingES$QE,
               SA_SMDH_no_inferential$QE),

  k_effect_sizes = c(SA_lnRR_published$k,
               SA_lnRR_no_comp3$k,
               SA_lnRR_flagged$k,
               SA_lnRR_no_missingES$k,
               SA_lnRR_flagged_no_missingES$k,
               SA_lnRR_geary_passed$k,
               SA_SMDH_published$k,
               SA_SMDH_no_comp3$k,
               SA_SMDH_flagged$k,
               SA_SMDH_no_missingES$k,
               SA_SMDH_flagged_no_missingES$k,
               SA_SMDH_no_inferential$k),

  n_studies = c(length(SA_lnRR_published$s.levels.f[[1]]),
               length(SA_lnRR_no_comp3$s.levels.f[[1]]),
               length(SA_lnRR_flagged$s.levels.f[[1]]),
               length(SA_lnRR_no_missingES$s.levels.f[[1]]),
               length(SA_lnRR_flagged_no_missingES$s.levels.f[[1]]),
               length(SA_lnRR_geary_passed$s.levels.f[[1]]),
               length(SA_SMDH_published$s.levels.f[[1]]),
               length(SA_SMDH_no_comp3$s.levels.f[[1]]),
               length(SA_SMDH_flagged$s.levels.f[[1]]),
               length(SA_SMDH_no_missingES$s.levels.f[[1]]),
               length(SA_SMDH_flagged_no_missingES$s.levels.f[[1]]),
               length(SA_SMDH_no_inferential$s.levels.f[[1]])
               ))

# Combine CI and PI into a single column each for compactness
SA_intercept_only <- SA_intercept_only %>%
  mutate(
    CI = paste0("[", sprintf("%.3f", CI_Lower), ", ", sprintf("%.3f", CI_Upper), "]"),
    PI = paste0("[", sprintf("%.3f", PI_Lower), ", ", sprintf("%.3f", PI_Upper), "]"),
    P_value = scales::pvalue(P_value),
    Q_value = sprintf("%.2f", Q_value)
  ) %>%
  select(
    effect_size,
    data_used,
    Estimate,
    CI,
    PI,
    P_value,
    k_effect_sizes,
    n_studies
  )

# Let's make this table pretty
SA_intercept_only<-SA_intercept_only%>%
  gt()%>%
  tab_options(
    table.font.size = px(12),
    table.border.top.color = "black",
    table.border.bottom.color = "black",
    heading.title.font.size = px(14),
    heading.subtitle.font.size = px(12),
    column_labels.font.weight = "bold"
  ) %>%
  tab_header(
    title = md("**Summary of Sensitivity Analyses for lnRR and SMD(H) Intercept-only models**")
  ) %>%
  cols_label(
    effect_size = "Effect Size",
    data_used = "Data used in model",
    Estimate = "Estimate",
    CI = "95% CI",
    PI = "95% PI",
    P_value = "P-value",
    k_effect_sizes = "k (No. of Effect Sizes)",
    n_studies = "n (No. of Studies)"
  ) %>%
  fmt_number(
    columns = c(Estimate),
    decimals = 3
  ) %>%
  tab_style(
    style = cell_borders(
      sides = "bottom",
      color = "black",
      weight = px(1)
    ),
    locations = cells_body()
  ) %>%
  tab_options(
    table.font.size = "small",
    heading.title.font.size = 14,
    table.border.top.width = px(2),
    column_labels.font.weight = "bold",
    row_group.font.weight = "bold"
  ) %>%
  opt_table_outline()

# Saving as an image
gtsave(SA_intercept_only, here::here("tables/SA_intercept_only.png"))

# For saving as a docx file
# gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.docx"))
# gtsave(SA_intercept_only,here::here("tables/SA_intercept_only.html"))
```

```{r Table for lnRR rho sensitivity analysis}

# t4 <- data.frame(rho  = rho_range,
#                  "overall effect"  = sapply(lnRR_VCV_range, function(x) coef(x)),
#                  "standard error" = sapply(lnRR_VCV_range, function(x) x$se),
#                  "p-value" = sapply(lnRR_VCV_range, function(x) x$pval),
#                  "Lower CI" = sapply(lnRR_VCV_range, function(x) x$ci.lb),
#                  "Upper CI" = sapply(lnRR_VCV_range, function(x) x$ci.ub),
#                  "Log-likehood" = sapply(lnRR_VCV_range, function(x) fitstats(x)[1,1]),
#                  "AIC" = sapply(lnRR_VCV_range, function(x) fitstats(x)[3,1]),
#                  "BIC" = sapply(lnRR_VCV_range, function(x) fitstats(x)[4,1]),
#                  "AICc" = sapply(lnRR_VCV_range, function(x) fitstats(x)[5,1]))
# 
# colnames(t4) <- c("Sampling correlation", "Overall effect (lnRR)", "Standard error", "p-value", "Lower CI", "Upper CI", "Log-likehood", "AIC", "BIC", "AICc")
# 
# t4 %>% dfround(4) %>% DT::datatable()
```

## Table: RoB Meta-regressions

# Loading models for blinding performed or not
lnRR_blinding<-readRDS(here::here("model/lnRR_blinding.rds"))
SMDH_blinding<-readRDS(here::here("model/SMDH_blinding.rds"))
